Selecting and ranking interesting pairs of cyclic temporal granularities

### 2020-11-19 main.Rmd
normalisation structure

### Distance measure

@@

### Distribution of $MMPD_{raw}$
<!-- ### Need for normalisation -->

@@

### Normalize distances

@@

Median and maximum distances are not robust to the number of levels and the metric would have higher values for harmonies with higher levels. Figure \ref{fig:mean-sd-max} shows how both mean and standard deviation of the distribution of maximum and median varies for different sample sizes ($n$). There is a rightward shift in the location and decrease in scale with increasing $n$. Thus these median maximum pairwise distances need to be normalized for different harmonies in a way that eliminates the effect of different levels, consequently enabling comparison across different harmonies. The Fisher–Tippett–Gnedenko theorem in the field of Extreme Value Theory states that the maximum of a sample of iid random variables after proper re-normalization can converge in distribution to only one of Weibull, Gumbel or Freschet distribution, independent of the underlying data or process.

More formally, $d_{1},d_{2}\ldots ,d_{n}$ be a sequence of independent and identically-distributed pairwise distances and $M_{n}=\max\{d_{1},\ldots ,d_{n}\}$. Then Fisher–Tippett–Gnedenko theorem [@De_Haan2007-yx] suggests that if a sequence of pairs of real numbers $(a_{n}, b_{n})$ exists such that each $a_{n}>0$ and $\lim _{{m\to \infty }}P\left({\frac  {M_{n}-b_{n}}{a_{n}}}\leq x\right)=F(x)$, where $F$ is a non-degenerate distribution function, then the limit distribution $F$ belongs to either the Gumbel, Fréchet or Weibull family. The normalizing constants $(a_{n}, b_{n})$ vary depending on the underlying distribution of the pairwise distances. Hence to normalize appropriately, it is 
important to assume a distribution of these distances.

For large $n$, the distribution of $M$ approaches a standard shape. But what about the case when $n$ is not large enough? The distribution of maximum in that case will indeed depend on $n$ and the underlying distribution of $D$. For large $n$, we could use EVT and CLT to normalise for $n$, however, most of the cyclic granularities encountered in practice have low $n$. Hence, normalisation could be done by bootstrapping procedure to ensure that the distribution of maximum/median have the same mean and variation for varying $n$.

```{r create_simdata}

```{r create_nlevels}

```{r norm_max_new}

```{r mean-sd-max, fig.cap = "Display shows mean and standard deviation of the distribution of maximum for sample sizes ranging from 2 to 30. There is a right shift in the distribution of maximum and median with increasing sample sizes."}

library(ggridges)
library(viridis)
max_all_data <- create_nlevels(nlevels = seq(2, 30, 2),
                           nsim = 500,
                           sim_dist = distributional::dist_normal(5, 10), create_fun = max)

g1 <- max_all_data %>% ggplot() + geom_density_ridges(aes(x=sim_data, y = as.factor(ind))) + ylab("n") + xlab("max")

median_all_data <- create_nlevels(nlevels = seq(2, 30, 2),
                           nsim = 500,
                           sim_dist = distributional::dist_normal(5, 10), create_fun = median)

g2 <- max_all_data %>% ggplot() + geom_boxplot(aes(x=sim_data, y = as.factor(ind)))  + ylab("n") + xlab("median")

ggpubr::ggarrange(g1, g2, ncol = 2)

## Performance

# Simulation study

@@

## Simulated designs

@@

## Environment

@@

## Experimental set up

@@

## Data Shuffling method

@@

### Method 1:

@@

### Method 2:

@@

>>>>

### Algorithm

@@

### Distribution
<!-- ### Need for normalisation -->

@@

## Methodology

@@

<!-- Median and maximum distances are not robust to the number of levels and the metric would have higher values for harmonies with higher levels. Figure \ref{fig:mean-sd-max} shows how both mean and standard deviation of the distribution of maximum and median varies for different sample sizes ($n$). There is a rightward shift in the location and decrease in scale with increasing $n$. Thus these median maximum pairwise distances need to be normalized for different harmonies in a way that eliminates the effect of different levels, consequently enabling comparison across different harmonies. The Fisher–Tippett–Gnedenko theorem in the field of Extreme Value Theory states that the maximum of a sample of iid random variables after proper re-normalization can converge in distribution to only one of Weibull, Gumbel or Freschet distribution, independent of the underlying data or process. -->

<!-- More formally, $d_{1},d_{2}\ldots ,d_{n}$ be a sequence of independent and identically-distributed pairwise distances and $M_{n}=\max\{d_{1},\ldots ,d_{n}\}$. Then Fisher–Tippett–Gnedenko theorem [@De_Haan2007-yx] suggests that if a sequence of pairs of real numbers $(a_{n}, b_{n})$ exists such that each $a_{n}>0$ and $\lim _{{m\to \infty }}P\left({\frac  {M_{n}-b_{n}}{a_{n}}}\leq x\right)=F(x)$, where $F$ is a non-degenerate distribution function, then the limit distribution $F$ belongs to either the Gumbel, Fréchet or Weibull family. The normalizing constants $(a_{n}, b_{n})$ vary depending on the underlying distribution of the pairwise distances. Hence to normalize appropriately, it is  -->
<!-- important to assume a distribution of these distances.  -->

<!-- For large $n$, the distribution of $M$ approaches a standard shape. But what about the case when $n$ is not large enough? The distribution of maximum in that case will indeed depend on $n$ and the underlying distribution of $D$. For large $n$, we could use EVT and CLT to normalise for $n$, however, most of the cyclic granularities encountered in practice have low $n$. Hence, normalisation could be done by bootstrapping procedure to ensure that the distribution of maximum/median have the same mean and variation for varying $n$. -->

<!-- ```{r create_simdata} -->

<!-- ```{r create_nlevels} -->

<!-- ```{r norm_max_new} -->

<!-- ```{r mean-sd-max, fig.cap = "Display shows mean and standard deviation of the distribution of maximum for sample sizes ranging from 2 to 30. There is a right shift in the distribution of maximum and median with increasing sample sizes."} -->

<!-- library(ggridges) -->
<!-- library(viridis) -->
<!-- max_all_data <- create_nlevels(nlevels = seq(2, 30, 2), -->
<!--                            nsim = 500, -->
<!--                            sim_dist = distributional::dist_normal(5, 10), create_fun = max) -->

<!-- g1 <- max_all_data %>% ggplot() + geom_density_ridges(aes(x=sim_data, y = as.factor(ind))) + ylab("n") + xlab("max") -->

<!-- median_all_data <- create_nlevels(nlevels = seq(2, 30, 2), -->
<!--                            nsim = 500, -->
<!--                            sim_dist = distributional::dist_normal(5, 10), create_fun = median) -->

<!-- g2 <- max_all_data %>% ggplot() + geom_boxplot(aes(x=sim_data, y = as.factor(ind)))  + ylab("n") + xlab("median") -->

<!-- ggpubr::ggarrange(g1, g2, ncol = 2) -->

## Simulation study

@@

### Simulated designs

@@

### Environment

@@

### Experimental set up

@@

### Data Shuffling method

@@

#### Method 1:

@@

#### Method 2:

@@

### Performance of normalised MMPD

```{r}
